---
title: "R-Bootcamp - Analysis of Building Projects in Zurich"
author: "Keith Lawless, Daniel Leibrock"
date: "2022-08-29"
output:
  html_document:
    toc: yes
    toc_depth: '3'
    df_print: paged
  pdf_document:
    toc: yes
    toc_depth: 3
subtitle: "MSC.IDS - HSLU Lucerne"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv("Data/BAU502OD5023.csv", encoding = "UTF-8")
prices <- read.csv("Data/BAU514OD5142.csv")
location <- read.csv("Data/stzh.adm_statzonen_beschr_p.csv")
```

```{r packages, include=FALSE}
library(dplyr)
library(shiny)
library(knitr)
library(ggplot2)
library(forecast)
library(kableExtra)
library(gridExtra)
library(formattable)
library(reshape2)
```

## Introduction to the Analysis

### Selection of the dataset

The dataset we want to analyze in the cause of this project, is the "**Neubauwohnungen nach Bauprojektstatus, Eigentumsart und statistischer Zone seit 2009**" dataset from the opendata.swiss website. The dataset contains information about housing projects in the city of Zurich since 2009 and holds information such as project status, ownership and location of the project. Furthermore, we add enriching data regarding real estate prices as well as adress data from the City of Zurich Open Data Portal to enrich our main dataset. 

......

### Goals of the Analysis

The goal of the Analysis is to get an insight into the development of the real estate market in Zurich throughout the past decade. We want to offer a diverse view on several aspects of the market, including the development of different types of projects, prices, owners and locations. Through this, we want to identify trends and offer an overview of the market structure.

### Research questions

Following the previous introduction and the goals of our analysis, we aim to answer the following research questions:

1) How did the number of overall building projects develop over time in different statistical zones / quartiers?
2) Who are the main owners / drivers of building projects?
3) Does the share of different building size groups change over time?
4) How did prices in the different parts of the city (quartiers) change over time?
5) Is there a relation between price development and building project development?

......


## Data Preparation

Data preparation consists of several steps. These include:

  - Deletion of obsolete columns from the different data sets
  - Renaming of several columns
  - Grouping and summarising of several columns 
  - Merging of the different datasets
  


```{r Prep_Main, echo = FALSE, include = FALSE}
drop_cols_data <- c("StatZoneSort", "QuarSort", "QuarCd", "KreisSort", "KreisCd", "ProjStatusSort", "EigentumsartSort")

datareduced <- data %>%
  select(- all_of(drop_cols_data)) %>%
  group_by(Jahr, KreisLang, QuarLang, StatZoneCd,ProjStatus, Eigentumsart, AnzWhg) %>%
  summarise(WhgSum = sum(AnzWhg))

#head(datareduced, n = 10)

datareduced_2 <- data %>%
  select(- all_of(drop_cols_data)) %>%
  group_by(Jahr, KreisLang) %>%
  summarise(WhgSum = sum(AnzWhg))

#head(datareduced_2, n = 40)

#write.csv(datareduced, "main.csv", fileEncoding = "UTF-8")
```

```{r Prep_Prices, echo = FALSE, include = FALSE}
drop_cols_prices <- c("QuarCd", "ZoneSort", "FrQmBodenNettoGanzeLieg", "FrQmBodenNettoStwE", "FrQmBodenNettoAlleHA")
price_cols <- c("FrQmBodenGanzeLieg", "FrQmBodenStwE", "FrQmBodenAlleHA", "FrQmWohnflStwE")
price_cols_renamed <- c("CHF / $m^{2}$ Boden (Ganze Liegensch.)", "CHF / $m^{2}$ Boden (Stockwerkb.)", "CHF / $m^{2}$ Boden (Kombiniert)", "CHF / $m^{2}$ Wohnfläche (Stockwerkb.)")

pricesreduced <- prices %>%
  select(- all_of(drop_cols_prices)) %>%
  filter(Typ != "Zahl") %>%
  mutate(FrQmBodenGanzeLieg = replace(FrQmBodenGanzeLieg, FrQmBodenGanzeLieg == ".", "")) %>%
  mutate(FrQmBodenStwE = replace(FrQmBodenStwE, FrQmBodenStwE == ".", "")) %>%
  mutate(FrQmBodenAlleHA = replace(FrQmBodenAlleHA, FrQmBodenAlleHA == ".", "")) %>%
  mutate(FrQmWohnflStwE = replace(FrQmWohnflStwE, FrQmWohnflStwE == ".", "")) %>%
  mutate_at(price_cols, as.integer) %>%
  group_by(QuarLang, Jahr) %>%
  summarise_at(price_cols, mean, na.rm = TRUE)
  
#head(pricesreduced, n = 50)

#write.csv(pricesreduced, "pricesreduced.csv", fileEncoding = "UTF-8")
#typeof(prices$FrQmBodenGanzeLieg)
#str(pricesreduced)
```



```{r Prep_Locations, echo = FALSE, include = FALSE}
#head(location, n = 10)
#summary(location)

drop_cols_location <- c("objid", "name", "ori", "hali", "vali")

location <- location %>%
  select(- all_of(drop_cols_location))
```


```{r Merge, echo = FALSE, include = FALSE}
datacomb <- left_join(datareduced, pricesreduced, by = c("QuarLang" = "QuarLang", "Jahr" = "Jahr"))
#head(datacomb, n = 10)

datafinal <- left_join(datacomb, location, by = c("StatZoneCd" = "kuerzel"))
head(datafinal, n = 100)

#write.csv(datafinal, "datafinal.csv", encoding = "UTF-8")
#readr::write_excel_csv(datafinal, "datafinal.csv")
```

## Exploratory Data Analysis

```{r EDA, echo = FALSE, include = FALSE}
summary(datafinal)
ImBau <- datafinal %>% 
  filter(ProjStatus == "Im Bau")
Bewilligt <- datafinal %>% 
  filter(ProjStatus == "Bewilligt")

sum(ImBau$AnzWhg) 
sum(Bewilligt$AnzWhg)
sapply(datafinal, function(x) n_distinct(x))
str(datafinal)
summary(datafinal)
```

The summary of the final dataframe reveals several insights about the general structure of the data as well as the real estate market itself. 

Regarding the general structure of the data, we can see that in total **27950 different datapoints** spread over a period of 13 years from **2009 until 2021**. In total, projects with a volume of **51016 apartments received approval** while **69194 appartments started construction** in Zurich during this period.  
*It is not clear, if individual apartments can appear in both categories at different points of time.*
 
The projects are located within **12 "Kreise" / regions**,  split into **34 "Quartiere" / districts** which are then again differentiated into **215 statistical zones**, the most granular geo-statistical level for the city of Zurich. While data about the number of apartments and geographic coordinates is available on this level, price data is only available on Quartier-level. Furthermore, the projects are assigned to **5 different types of ownership**.  


<br/>

## Visual Data Analysis  

In this chapter, we want to visually analyze the structure of the real estate market. Lorem ipsum...

```{r Test, echo = FALSE, eval = FALSE}
testplot <-
  ggplot(data = datareduced_2,
         mapping = aes(y = WhgSum, x = Jahr, colour = KreisLang)) + geom_line()

testplot
```

```{r Price_table, echo = FALSE}
cols <- c("Jahr", "QuarLang", "FrQmBodenGanzeLieg", "FrQmBodenStwE", "FrQmBodenAlleHA", "FrQmWohnflStwE")
price_cols_renamed <- c("CHF / $m^{2}$ Boden (Ganze Liegensch.)", "CHF / $m^{2}$ Boden (Stockwerkb.)", "CHF / $m^{2}$ Boden (Kombiniert)", "CHF / $m^{2}$ Wohnfläche (Stockwerkb.)")
kreis_renamed <- c(1:12)

pricetable <- datafinal %>% 
  rename_at(all_of(price_cols), function(x) price_cols_renamed) %>% 
  rename(Quartier = QuarLang) %>% 
  rename(Kreis = KreisLang) %>%  
  group_by(Jahr, Kreis, Quartier) %>% 
  summarise_at(price_cols_renamed, mean, na.rm = TRUE)

yearprices <- pricetable %>% 
  group_by(Jahr) %>% 
  summarise_at(price_cols_renamed, mean, na.rm = TRUE)

kreisprices <- pricetable %>% 
  group_by(Kreis) %>%
  summarise_at(price_cols_renamed, mean, na.rm = TRUE)

quartierprices <- pricetable %>% 
  group_by(Quartier) %>% 
  summarise_at(price_cols_renamed, mean, na.rm = TRUE)
```

### Price developments and differences

#### Average price development per sq.m. of condominium ownership and ground (CHF)
<br/>

As a first visual analysis of the data we will look at price developments on different levels. We want to get an overview of the development of yearly-averaged prices over time, split in the different categories available. These are CHF / $m^{2}$ Boden (Ganze Liegenschaft), CHF / $m^{2}$ Boden (Stockwerkbesitz), CHF / $m^{2}$ Boden (Kombiniert) as well as CHF / $m^{2}$ Wohnfläche (Stockwerkbesitz). 

**The following table and plot show information about real estate prices averaged over the whole city of Zurich for each year in CHF:**  
<br/><br/>

```{r yearprices, echo = FALSE}
formattable(yearprices,
            "Jahr" = list(color = "grey", font.weight = "bold"))
```

<br/><br/>

```{r yearprices_plot, echo = FALSE, warning = FALSE, message = FALSE}
ggplot(yearprices, aes(x = Jahr)) +
  geom_smooth(span = .2, aes(y = `CHF / $m^{2}$ Wohnfläche (Stockwerkb.)`), size = 1, color = "brown2") +
  geom_smooth(span = .2, aes(y = `CHF / $m^{2}$ Boden (Stockwerkb.)`), size = 0.5, linetype = "dashed") +
  geom_smooth(span = .2, aes(y = `CHF / $m^{2}$ Boden (Ganze Liegensch.)`), size = 0.5, linetype = "dashed") +
  geom_smooth(span = .2, aes(y = `CHF / $m^{2}$ Boden (Kombiniert)`), size = 1) + 
  geom_smooth(aes(y = `CHF / $m^{2}$ Wohnfläche (Stockwerkb.)`), method = "lm", size = 1, color = "brown2", se = FALSE, linetype = "dashed") +
  geom_smooth(aes(y = `CHF / $m^{2}$ Boden (Kombiniert)`), method = "lm", size = 1, se = FALSE, linetype = "dashed") +
  theme(
    panel.grid.major = element_line(colour = "gray80"),
    panel.grid.minor = element_line(colour = NA),
    axis.text = element_text(family = "sans",
                             face = "bold"),
    panel.background = element_rect(fill = "white")
  ) +
  ylab("") +
  xlab("")

```

As we can see, the overall price trend is clearly upwards. The red curve, which represents the price for living space / Wohnfläche in condominium ownership / Stockwerkbesitz, is showing a continuous and constant **growth of about 575 CHF per year** over the observed timeline. The thick blue curve, which represents the price for ground / Boden, combined for both Stockwerkbesitz (upper dashed, blue line) and whole buildings / ganze Liegenschaft (lower dashed, blue line), reveals a yearly average **price increase of about 1000 CHF**.  
<br/><br/>

#### Average price per sq.m. of condominium ownership and ground (CHF) per Kreis  
<br/><br/>

```{r kreisprices, echo = FALSE}
formattable(kreisprices,
            "Kreis" = list(color = "grey", font.weight = "bold"))
```

<br/><br/>

```{r kreisprices_plot, echo = FALSE}
dfm <- melt(kreisprices[,c('Kreis','CHF / $m^{2}$ Wohnfläche (Stockwerkb.)','CHF / $m^{2}$ Boden (Kombiniert)')],id.vars = 1)
dfm <- dfm %>% 
    mutate(across(where(is.factor), as.character)) %>%
    mutate(variable = replace(variable, variable == "CHF / $m^{2}$ Wohnfläche (Stockwerkb.)", "Preis / qm. Wohnfläche")) %>% 
    mutate(variable = replace(variable, variable == "CHF / $m^{2}$ Boden (Kombiniert)", "Preis / qm. Boden"))

ggplot(dfm, aes(x = reorder(Kreis, -value), y = value)) + 
    geom_bar(aes(fill = variable), stat = "identity", position = "dodge") + 
    scale_y_continuous() +
    ylab("") +
    xlab("") + 
    theme(panel.grid.major = element_line(colour = "gray80"), legend.title = element_text(colour = NA), 
      panel.background = element_rect(fill = "white")) +labs(x = NULL, y = NULL) + theme(legend.position = "top")

plot_1 <- 
  ggplot(kreisprices) +
    aes(x = Kreis, fill = Kreis) +
    geom_col(aes(y = `CHF / $m^{2}$ Wohnfläche (Stockwerkb.)`), show.legend = FALSE) +
    scale_fill_hue(direction = 1) +
    xlab("") +
    ylab("")

plot_2 <-
  ggplot(kreisprices) +
    aes(x = Kreis, fill = Kreis) +
    geom_col(aes(y = `CHF / $m^{2}$ Boden (Kombiniert)`), show.legend = FALSE) +
    scale_fill_hue(direction = 1) +
    xlab("") +
    ylab("")

#grid.arrange(plot_1, plot_2, nrow = 1)
```


### Special Topic: Mapping / Shiny

```{r VDA_2}

```

## Modelling and Prediction

### Model XYZ

```{r Model}

```

### Prediction XYZ

```{r Prediction}

```

## Summary and Conclusion

